### 2012-11-09 inst/examples/testing-gp-sdp.Rmd
updated examples using sequential approach
show figures

```{r libraries}
require(pdgControl)
require(nonparametricbayes)
require(ggplot2)
opts_knit$set(upload.fun = socialR::flickr.url)
```

@@

>>>>

```{r libraries}
require(pdgControl)
require(nonparametricbayes)
require(ggplot2)
opts_knit$set(upload.fun = socialR::notebook.url)
```

@@

```{r}
#escapement <- Vectorize(function(i,j) pmax(0, x_grid[i] - h_grid[D[j,(Tmax-t+1)]]))
#S <- outer(1:n_x, 1:n_h, escapement)
```
